Printing in a Periphery: a Quantitative Study of Finnish Knowledge Production, 1640-1828

### 2017-02-13 inst/examples/20170201-manuscript.Rmd
manuscript figures
ok

### Fig. 1: Number of publication places per decade

@@

### Fig 2: Number of documents per decade

@@

### Fig 3: Rise of the octavo sized book as vehicle of Enlightenment

Paper consumption: different document formats over time

@@

### Fig 5: Turku in Sweden: proportions for title count and paper in Swedish University towns

@@

### Fig. 7: Riksdagar Kungliga

@@

### Fig. 8: Riksdagar Fennica

@@

### Fig 9A: Fennica - Publishers in Swedish University towns (and Finland)

@@

### Fig 9B: Kungliga - Publishers in Swedish University towns (and Finland)

@@

### Fig 10: Publications in Vaasa in Fennica, 1750-1828, with percentage of all books that were not published by the printing house of the court

@@

### IMAGE 12: Title count per capita

@@

### Fig 13 Octavo paper consumption

@@

### Fig 14: Octavo title length

@@

### Fig 15: Different languages in Turku, Stockholm, Uppsala and Lund

@@

### Fig 16: Topic richness per language (publications in Fennica)

@@

### Fig 17: Temporary sermons in Latin and Swedish

@@

### Fig 18: Devotional literature (catechisms, hymns, prayers, etc.)

@@

### Fig 19: Publisher per city over time

>>>>

### Fig. 1: Number of publication places over time

@@

### Fig 2: Title count over time

@@

### Fig 3: Rise of the Octavo

Paper consumption for various document formats over time.

@@

### Fig 5: Turku as Swedish university town

Proportions for title count and paper in Swedish University towns

@@

### Fig. 7: Riksdagar: Kungliga

@@

### Fig. 8: Riksdagar: Fennica

@@

### Fig 9A: Fennica: Publishers in Swedish University towns (and Finland)

@@

### Fig 9B: Kungliga: Publishers in Swedish University towns (and Finland)

@@

### Fig 10: Publications in Vaasa in Fennica, 1750-1828

With percentage of all books that were not published by the printing house of the court.

@@

### Fig. 12: Title count per capita

@@

### Fig. 13: Octavo paper consumption

@@

### Fig. 14: Octavo title length (word count)

@@

### Fig 15: Language use in Turku, Stockholm, Uppsala and Lund

@@

### Fig. 16: Topic richness per language (Fennica)

@@

### Fig. 17: Temporary sermons in Latin and Swedish

@@

### Fig. 18: Devotional literature (catechisms, hymns, prayers, etc.)

@@

### Fig. 19: Publisher per city over time
